Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-02 treestats_paper.tex

>>>>

\begin{figure}

% Run the script illustrate_algorithm.py to generate these pdfs and
% the latex tables below.
\begin{center}
\begin{tabular}{ccc}
\includegraphics[width=4cm]{figures/tree_0_init.pdf} & &
\includegraphics[width=4cm]{figures/tree_0_out_0.pdf}
\\

\begin{tabular}{c|cccc}
& $\pi$ & $\beta$ & $x$ & $F$\\
\hline
0 & 8 & 4.0 & 1.0 & 0.2\\
1 & 5 & 1.0 & 1.0 & 0.2\\
2 & 5 & 1.0 & 1.0 & 0.2\\
3 & 6 & 2.0 & 1.0 & 0.2\\
4 & 6 & 2.0 & 1.0 & 0.2\\
5 & 7 & 2.0 & 2.0 & 0.3\\
6 & 7 & 1.0 & 2.0 & 0.3\\
7 & 8 & 1.0 & 4.0 & 0.2\\
8 & -1 & 0.0 & 5.0 & 0.0\\
\end{tabular}
& &
\begin{tabular}{c|cccc}
& $\pi$ & $\beta$ & $x$ & $F$\\
\hline
0 & 8 & 4.0 & 1.0 & 0.2\\
1 & 5 & 1.0 & 1.0 & 0.2\\
2 & 5 & 1.0 & 1.0 & 0.2\\
3 & 6 & 2.0 & 1.0 & 0.2\\
4 & 6 & 2.0 & 1.0 & 0.2\\
5 & 7 & 2.0 & 2.0 & 0.3\\
6 & -1 & 0.0 & 2.0 & 0.3\\
7 & 8 & 1.0 & 2.0 & 0.3\\
8 & -1 & 0.0 & 3.0 & 0.3\\
\end{tabular}
\\
(A) && (B)
\end{tabular}
\end{center}

\caption{
\label{fig:algorithm_example}
Illustration of the internal state for algorithm B for $\iw = \bone_S$ and
$f(x) = x(5 - x) / 20$ as in Example~\ref{ex:site_diversity}. (A)
Immediately before we remove the edge joining 6 to 7 and (B) immediately after.
See the text for descriptions of the arrays encoding the state.}
\end{figure}
